### 2017-05-09 02-background.tex
Some nitpicks

\paragraph{\textbf{Sampling global parameters}} The update rule for global parameter $\theta$ is
\bea
\ta_{ki}^* \law \left| \ta_{ki} + \f{\ep}{2} \left( \eta - \ta_{ki} + h(\Minibatcht)\sum_{(a,b) \in \Minibatcht}g_{ab}(\ta_{ki})\right) \right.\nn \\ \left.+ (\ta_{ki})^{\ha}\xi_{ki} \right|, \label{eqn:global_update}
\eea
where the gradient in $\theta$ is
\bea
g_{ab}(\ta_{ki})
&=& \f{f_{ab}^{(y)}(k,k)}{Z_{ab}^{(y)}} \left(\f{|1-i-y|}{\ta_{ki}} - \f{1}{\sum_j\ta_{kj}} \right),
\eea
here $\Minibatcht$ is a mini-batch of $n_t$ vertex pairs sampled from $\Edges$ or $E$; $h(\Minibatcht)$ is a weight factor to scale the effect of a mini-batch towards the full network; and 
\bea
f_{ab}^{(y)}(k,l)=
\begin{cases}
\bt_k^y(1-\bt_k)^{(1-y)}\pi_{ak}\pi_{bk}, & \mbox{if } k=l\\
\dt^{y}(1-\dt)^{(1-y)} \pi_{ak} \pi_{bl}, & \mbox{if } k \neq l \nn.
\end{cases}
\label{eqn:case}
\eea
$Z_{ab}^{(y)}$ is the normalization constant which we can compute in $\cO(K)$ time \cite{LiAW15}.

\paragraph{\textbf{Sampling local parameters}}
The update rule for the local parameters $\phi$ is
\bea
\phi_{ak}^* \law \left| \phi_{ak} + \f{\ep}{2} \left( \al - \phi_{ak} + \f{N}{|\Neighbors|} \sum_{b \in \Neighbors} g_{ab}(\phi_{ak})\right) \right. \nn \\ \left. + (\phi_{ak})^{\ha} \xi_{ak}\right|,
\label{eqn:local_update}
\eea
where the gradient in $\phi$ is
\bea
g_{ab}(\phi_{ak}) = \f{f_{ab}^{(y)}(k)}{Z_{ab}^{(y)}\phi_{ak}} - \f{1}{\sum_j\phi_{aj}}.
\eea
Here, $\Neighbors$ is the neighbor set for a mini-batch node, another random mini-batch of $n$ nodes sampled from \Vertices. Note that $|\Neighbors| \ll |\Vertices|=N$.

>>>>

\paragraph*{\textbf{Sampling global parameters}} the update rule for global parameter $\theta$ is
\bea
\ta_{ki}^* \law \left| \ta_{ki} + \f{\ep}{2} \left( \eta - \ta_{ki} + h(\Minibatcht)\sum_{(a,b) \in \Minibatcht}g_{ab}(\ta_{ki})\right) \right.\nn \\ \left.+ (\ta_{ki})^{\ha}\xi_{ki} \right|, \label{eqn:global_update}
\eea
where the gradient in $\theta$ is
\bea
g_{ab}(\ta_{ki})
&=& \f{f_{ab}^{(y)}(k,k)}{Z_{ab}^{(y)}} \left(\f{|1-i-y|}{\ta_{ki}} - \f{1}{\sum_j\ta_{kj}} \right),
\eea
here $\Minibatcht$ is a mini-batch of $n_t$ vertex pairs sampled from $\Edges$ or $E$; $h(\Minibatcht)$ is a weight factor to scale the effect of a mini-batch towards the full network; and 
\bea
f_{ab}^{(y)}(k,l)=
\begin{cases}
\bt_k^y(1-\bt_k)^{(1-y)}\pi_{ak}\pi_{bk}, & \mbox{if } k=l\\
\dt^{y}(1-\dt)^{(1-y)} \pi_{ak} \pi_{bl}, & \mbox{if } k \neq l \nn.
\end{cases}
\label{eqn:case}
\eea
$Z_{ab}^{(y)}$ is the normalization constant which we can compute in $\cO(K)$ time \cite{LiAW15}.

\paragraph*{\textbf{Sampling local parameters}}
the update rule for the local parameters $\phi$ is
\bea
\phi_{ak}^* \law \left| \phi_{ak} + \f{\ep}{2} \left( \al - \phi_{ak} + \f{N}{|\Neighbors|} \sum_{b \in \Neighbors} g_{ab}(\phi_{ak})\right) \right. \nn \\ \left. + (\phi_{ak})^{\ha} \xi_{ak}\right|,
\label{eqn:local_update}
\eea
where the gradient in $\phi$ is
\bea
g_{ab}(\phi_{ak}) = \f{f_{ab}^{(y)}(k)}{Z_{ab}^{(y)}\phi_{ak}} - \f{1}{\sum_j\phi_{aj}}.
\eea
Here, $\Neighbors$ is the neighbor set for a mini-batch node, another random mini-batch of $n$ nodes sampled from \Vertices. Note that $|\Neighbors| \ll |\Vertices|=N$.

### 2017-05-09 gpu-03-problem-statement.tex
Place the chunks of text unmodified into one document
Some nitpicks

In this section we describe the computational aspects of the SG-MCMC MMSB
algorithm. Moreover, we will introduce the data structures and notation that
will be used throughout this paper.
%
Kindly refer to~\cite{DBLP:journals/corr/LiAW15} for a detailed explanation of
the statistical concepts of the algorithm.

@@

\begin{figure}[tb]
\input{03-02-algorithm}
\end{figure}

The first stage (line~2 in the listing) randomly draws a mini-batch $M$,
using the "stratified random node" strategy~\cite{DBLP:journals/corr/LiAW15}.
In this strategy, a coin toss is used to decide between two sample types.
%
The first sample type
chooses one random vertex $i$ and selects all of its edges to constitute the
mini-batch $M$. This sample type is referred to as \textit{link edges}. On the other
hand, the second sample type randomly draws a vertex $i$ and generates
random edges of the form ($i$, $j$) such that the edges are not in $G$. This
sample type is referred to as \textit{nonlink edges}. The set of vertices that
constitute the edges of the mini-batch $M$ are represented by $m$.

@@

At regular intervals, the algorithm's global state is assessed by
evaluating the perplexity over the edges in the validation set $H$. The
\textit{perplexity} is a metric that represents the quality of the algorithm solution at
a given point in time. It is used to detect the algorithm's
convergence.
The
perplexity, as defined in~\cite{DBLP:journals/corr/LiAW15}, is the exponential
of the average over time of the negative
log-likelihood of meeting a link edge. In this 7th stage, $\beta$ is used,
as are $\pi_a$ and $\pi_b$ for each edge $(a,b)$ in~$H$.

>>>>

In this section we describe the computational aspects of the SG-MCMC MMSB
algorithm. Moreover, we will introduce the data structures and notation that
will be used throughout this paper.
%
Kindly refer to~\cite{LiAW15} for a detailed explanation of
the statistical concepts of the algorithm.

@@

\begin{figure}[tb]
\input{gpu-03-02-algorithm}
\end{figure}

The first stage (line~2 in the listing) randomly draws a mini-batch $M$,
using the "stratified random node" strategy~\cite{LiAW15}.
In this strategy, a coin toss is used to decide between two sample types.
%
The first sample type
chooses one random vertex $i$ and selects all of its edges to constitute the
mini-batch $M$. This sample type is referred to as \textit{link edges}. On the other
hand, the second sample type randomly draws a vertex $i$ and generates
random edges of the form ($i$, $j$) such that the edges are not in $G$. This
sample type is referred to as \textit{nonlink edges}. The set of vertices that
constitute the edges of the mini-batch $M$ are represented by $m$.

@@

At regular intervals, the algorithm's global state is assessed by
evaluating the perplexity over the edges in the validation set $H$. The
\textit{perplexity} is a metric that represents the quality of the algorithm solution at
a given point in time. It is used to detect the algorithm's
convergence.
The
perplexity, as defined in~\cite{LiAW15}, is the exponential
of the average over time of the negative
log-likelihood of meeting a link edge. In this 7th stage, $\beta$ is used,
as are $\pi_a$ and $\pi_b$ for each edge $(a,b)$ in~$H$.
